### 2024-01-23 output/paper.rmd
add

---
title: "zz"
format: html
editor: visual
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2024-01-23 01_downloaddata.R

@@ -1,0 +1,39 @@
+#### Preamble ####
+# Purpose: Get data on 2021 shelter usage and make table
+# Author: Rohan Alexander
+# Email: rohan.alexander@utoronto.ca
+# Date: 1 July 2022
+# Prerequisites: -
+
+#### Workspace setup ####
+install.packages("opendatatoronto")
+install.packages("knitr")
+install.packages("janitor")
+install.packages("lubridate")
+install.packages("tidyverse")
+
+library(knitr)
+library(janitor)
+library(lubridate)
+library(opendatatoronto)
+library(tidyverse)
+
+
+#### Acquire ####
+toronto_shelters <-
+  # Each package is associated with a unique id  found in the "For 
+  # Developers" tab of the relevant page from Open Data Toronto
+  # https://open.toronto.ca/dataset/daily-shelter-overnight-service-occupancy-capacity/
+  list_package_resources("21c83b32-d5a8-4106-a54f-010dbe49f6f2") |>
+  # Within that package, we are interested in the 2021 dataset
+  filter(name == 
+           "daily-shelter-overnight-service-occupancy-capacity-2021.csv") |>
+  # Having reduced the dataset to one row we can get the resource
+  get_resource()
+
+write_csv(
+  x = toronto_shelters,
+  file = "toronto_shelters.csv"
+)
+
+head(toronto_shelters)

### 2024-01-23 script/02_cleandata.R

@@ -1,0 +1,12 @@
+toronto_shelters_clean <-
+  clean_names(toronto_shelters) |>
+  mutate(occupancy_date = ymd(occupancy_date)) |> 
+  select(occupancy_date, occupied_beds)
+
+head(toronto_shelters_clean)
+
+write_csv(
+  x = toronto_shelters_clean,
+  file = "cleaned_toronto_shelters.csv"
+)
+

### 2024-01-23 01_downloaddata.R
haha

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Get data on 2021 shelter usage and make table
-# Author: Rohan Alexander
-# Email: rohan.alexander@utoronto.ca
-# Date: 1 July 2022
+# Purpose: covid19 cases
+# Author: Ziyi Liu
+# Email: jacqueline.liu@mail.utoronto.ca
+# Date: 23 January 2024
 # Prerequisites: -
 
 #### Workspace setup ####
@@ -17,23 +17,24 @@ library(janitor)
 library(lubridate)
 library(opendatatoronto)
 library(tidyverse)
+packages <- list_packages(limit = 10)
+packages
 
 
 #### Acquire ####
-toronto_shelters <-
-  # Each package is associated with a unique id  found in the "For 
-  # Developers" tab of the relevant page from Open Data Toronto
-  # https://open.toronto.ca/dataset/daily-shelter-overnight-service-occupancy-capacity/
-  list_package_resources("21c83b32-d5a8-4106-a54f-010dbe49f6f2") |>
-  # Within that package, we are interested in the 2021 dataset
-  filter(name == 
-           "daily-shelter-overnight-service-occupancy-capacity-2021.csv") |>
-  # Having reduced the dataset to one row we can get the resource
-  get_resource()
+toronto_covid <- search_packages("covid")
+toronto_covid
+covid1 <- list_package_resources("64b54586-6180-4485-83eb-81e8fae3b8fe")
+  
+covid_file <- covid1 %>% 
+  filter(name == "COVID19 cases.csv") 
+  
+View(covid_file)
+covid_data <- get_resource(covid_file)
 
 write_csv(
-  x = toronto_shelters,
-  file = "toronto_shelters.csv"
+  x = toronto_covid,
+  file = "toronto_covid.csv"
 )
 
-head(toronto_shelters)
+head(toronto_covid)

### 2024-01-23 02_cleandata.R

@@ -1,12 +1,20 @@
-toronto_shelters_clean <-
-  clean_names(toronto_shelters) |>
-  mutate(occupancy_date = ymd(occupancy_date)) |> 
-  select(occupancy_date, occupied_beds)
+library(readr)
+library(dplyr)
+library(lubridate)
 
-head(toronto_shelters_clean)
+# Read the dataset
+toronto_housing_data <- read_csv("toronto_housing.csv")
+
+# Clean the data
+toronto_housing_data_cleaned <- toronto_housing_data %>%
+  select(-civic_issues) %>%
+  mutate(last_refreshed = ymd(last_refreshed))
+
+# View the cleaned data
+head(toronto_housing_data_cleaned)
 
 write_csv(
-  x = toronto_shelters_clean,
-  file = "cleaned_toronto_shelters.csv"
+  x = toronto_housing_data_cleaned,
+  file = "cleaned_toronto_housing.csv"
 )
 

### 2024-01-23 01_downloaddata.R
ggg

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: covid19 cases
+# Purpose: Active Affordable and Social Housing Units
 # Author: Ziyi Liu
 # Email: jacqueline.liu@mail.utoronto.ca
 # Date: 23 January 2024
@@ -22,19 +22,20 @@ packages
 
 
 #### Acquire ####
-toronto_covid <- search_packages("covid")
-toronto_covid
-covid1 <- list_package_resources("64b54586-6180-4485-83eb-81e8fae3b8fe")
-  
-covid_file <- covid1 %>% 
-  filter(name == "COVID19 cases.csv") 
-  
-View(covid_file)
-covid_data <- get_resource(covid_file)
+toronto_housing <- search_packages("housing")
+toronto_housing
+housing1 <- list_package_resources("active-affordable-and-social-housing-units")
+housing1
+
+housing_file <- housing1 %>% 
+  filter(name == "Social and Affordable Housing.csv") 
+
+View(housing_file)
+housing_data <- get_resource(housing_file)
 
 write_csv(
-  x = toronto_covid,
-  file = "toronto_covid.csv"
+  x = toronto_housing,
+  file = "toronto_housing.csv"
 )
 
-head(toronto_covid)
+head(toronto_housing)

### 2024-01-24 output/paper.rmd
please work

@@
 ---
-title: "zz"
-format: html
-editor: visual
+title: "Exploring Urban Housing Dynamics: Challenges and Strategies in Toronto's Affordable and Social Housing Landscape"
+author: 
+  - Ziyi Liu
+thanks: "Code and data are available at: https://github.com/liuziy23/Ziyi-Liu.git"
+date: "`r format(Sys.time(), '%d %B %Y')`"
+abstract: "This paper delves into the multifaceted urban landscape of Toronto, focusing on the challenges and strategic responses linked with affordable and social housing.Toronto is one of the most populus and diverse cities in North Ameriva, it acts as a unique case study to examine urban housing dynamics.
+This research emoloys several dataset that p"
+output:
+  bookdown::pdf_document2
+toc: TRUE
+bibliography: reference.bib
 ---
 
-## Quarto
-
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
-
-## Running Code
-
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
-
-```{r}
-1 + 1
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+# Set up libraries
+library(tidyverse)
+library(janitor)
 ```
 
-You can add options to executable code like this
+\newpage
 
-```{r}
-#| echo: false
-2 * 2
+# Introduction
+
+As one of the busiest and most modern city in Canada, Toronto constantly faces a large number of citizens, and, inevitably, heavy traffic.
+The road condition in Toronto is busy most of the time.
+The vast majority of roads and buildings under construction that take place almost everywhere narrow the roadway of vehicles and turn off traffic lights [@cite4].
+Heavy traffic is likely to be one of the main reasons behind car accidents, because it increases the road rage and encourages the vehicle drivers to make dangerous moves to save time.
+Vehicle collisions have always brought large financial costs to the involving parties, and even more, they even brought injuries and deaths.
+In just 2019, traffic accidents resulted in more than 1700 deaths and more than 140000 injuries [@cite1].
+
+The Motor Vehicle Collisions data of Toronto provides a record of the past severe vehicle collisions in Toronto which result in injuries or deaths, and with the help of statistical data analysis, it can possibly offer insights on the ways to reduce this type of accident.
+This report investigates the motor vehicle collisions in Toronto from 2006 to 2020, with a focus on the ones result in injuries or deaths.
+In Section \@ref(motor-vehicle-collisions-involving-killed-or-seriously-injured-persons), the Motor Vehicle Collisions dataset is introduced and organized to visualize the change in the annual number of traffic accidents with respect to their fatality and their location.
+Then, I discussed about the possible implications of these visualizations.
+Figure 1 showed that there was a descending trend of traffic accidents from 2006 to 2020.
+By Figure 2, I concluded that motor vehicle collisions are always more likely to occur at intersections.
+Thus, I brought out the Red Light Cameras dataset in Section \@ref(red-light-cameras) to see whether if the number of red light cameras has an effect on the number of traffic accidents with serious injuries and deaths.
+The result from the datasets indicates that there is no clear relationship between this two factors, suggesting that just by installing more red light cameras cannot prevent traffic accidents from happening at intersections.
+More implications and further discussions on this result is presented in Section \@ref(discussion).
+
+# Data
+
+## Motor Vehicle Collisions involving Killed or Seriously Injured Persons
+
+To investigate the motor vehicle collisions in Toronto, I obtained the dataset "Motor Vehicle Collisions involving Killed or Seriously Injured Persons" from the Toronto Open Data Portal [@citedata].
+Provided by the Toronto Police Service, this dataset includes all vehicle collisions occurred in Toronto between 2006 and 2020 that result in injuries or deaths.
+One bias aroused by this dataset is the offset from the real accident location.
+For ethical reason and the protection of the parties involved in the accidents that are considered to be criminal cases, the location of those criminal accidents are offset to the closest intersection node [@citecollisiondata].
+As a result, the location of those accidents specific to neighborhoods might not be accurate.
+Therefore, I will use the variable district instead of the variable neighbourhood to categorize the accidents later in the report to avoid the bias.
+
+This dataset contains 16840 observations of collisions and 54 variables with all kinds of information of each collision.
+This report focuses on four of these variables which are: year, accident location, district, and fatality.
+By using R [@citeR], and R packages "tidyverse" [@citetidyverse], "dplyr" [@citedplyr], "janitor" [@citejanitor], "kableExtra" [@citekableExtra] and "knitr" [@citeknitr], an extract of the cleaned dataset (Table \@ref(tab:dataextract)) is shown below.
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+# Load motor vehicle collision data and clean
+vehicle_collision <- read_csv(here::here("inputs/data/vehicle_collisions.csv")) %>%
+  clean_names() %>%
+  drop_na(year) %>%
+  filter(acclass != "Property Damage Only")
 ```
 
-The `echo: false` option disables the printing of code (only output is displayed).
+```{r dataextract, echo=FALSE, message=FALSE}
+# Set up libraries
+library(knitr)
+library(kableExtra)
+
+# Create a table with selected columns
+vehicle_collision <- vehicle_collision %>%
+  select(year, accloc, district, acclass)
+vehicle_collision %>%
+  slice(1:10) %>%
+  kable(
+    caption = "Extracting the first ten rows from the Motor Vehicle Collisions data",
+col.names=c("Year", "Collision location", "District", "Fatality"),
+linesep = "", digits = 1, booktabs=TRUE) %>%
+  kable_styling(latex_options = "HOLD_position", font_size = 10)
+
+```
+
+Table \@ref(tab:dataextract) shows the first ten rows of the Motor Vehicle Collisions data.
+Variable "Year" indicates the year in which the accident occurs.
+Variable "District" provides the district of the accident.
+Variable "Collision location" includes 8 types: at intersection, intersection related, at/near private drive, laneway, non intersection, overpass or bridge, trail, and underpass or tunnel.
+Variable "Fatality" involves fatal and non-fatal injury.
+
+I'm interested in finding the trend of motor vehicle collisions from 2006 to 2020 and the types of injuries they result in.
+It reveals the traffic control in Toronto, and possibly the quality and knowledge of vehicle owners throughout these years.
+
+```{r echo=FALSE, fig.cap="Comparing the number of traffic collisions each year from 2006 to 2020", fig.width=8.4, fig.height=3.6}
+# Create a bar plot to show number of collisions by fatality
+ggplot(mapping = aes(x = year, fill = acclass), data=vehicle_collision) +
+  geom_bar()+theme_light()+ylab("number of motor vehicle collisions")+scale_fill_discrete(name = "Fatality")+facet_wrap(~acclass)
+```
+
+Figure 1 shows a descending pattern for the number of car accidents involving non-fatal injuries from year 2006 to 2020.
+The number of fatal accidents does not increase nor decrease much.
+In general, the number vehicle collisions in Toronto has largely decrease, indicating that when combining this two factors(number and fatality), Toronto has done a better job on traffic control in general.
+I'm also interested in the trend of motor vehicle collisions if other factors are taken into considerations.
+\newpage
+
+```{r echo=FALSE, fig.cap="Comparing the location of traffic collisions each year from 2006 to 2020", fig.width=6, fig.height=3.2}
+# Create a bar plot to show number of collisions by accident location
+ggplot(mapping = aes(x = year, fill=accloc), data=vehicle_collision)+scale_fill_discrete(name = "Accident location")+ylab("number of motor vehicle collisions")+theme_light()+geom_bar()
+```
+
+Figure 2 illustrates the where these vehicle collisions usually take place from 2006 to 2020.
+Before 2013, half of the data doesn't come with accident location, which is understandable because back in the days there wasn't an easy approach to record and save the data, so they often got lost.
+A large proportion of the accidents take place either at intersections or is intersection related.
+The other seven accident locations types add up to less than half of all vehicle collisions.
+At intersections, a lot more rule breaking behaviors can be committed by drivers.
+For instance, they could sometimes ignore stop signs, speed up when approaching yellow traffic lights; some even claimed that they rarely yielded at intersections.
+These behaviors largely increase the possibility of them colliding with other vehicles and the pedestrians at intersections.
+
+Motor vehicle collisions are most likely to take place at intersections.
+Thus, if measures are taken to restrict the driver's rule breaking behaviors at intersections, the numbers of car accidents would certainly drop a lot in general.
+Red light camera is claimed to be a measure taken by the government to monitor the vehicles at intersections.
+I will look into whether it's effective or not in respect of preventing the traffic accidents from happening.
+
+## Red Light Cameras
+
+The number of red light camera instilled in Toronto from 2007 to 2020 is obtained from the dataset "Red Light Cameras" found in the Toronto Open Data Portal [@citedata].
+This dataset is shared by the Transportation Services and it covers the locations of red light cameras in Toronto.
+In its introduction, this dataset claims that red light cameras can improve the safety of the drivers and pedestrians by monitoring the behavior of the drivers [@citecameradata].
+It contains 199 observations and 32 variables.
+This dataset's downside is that it is missing values in lots of its variables.
+To reduce errors generated from this downside, I will only utilize the variables with no missing values.
+R [@citeR], R packages "tidyverse" [@citetidyverse], "dplyr" [@citedplyr], "janitor" [@citejanitor], "kableExtra" [@citekableExtra] and "knitr" [@citeknitr] are used to produce an extract of the cleaned dataset (Table \@ref(tab:dadaextract1)).
+
+```{r dadaextract1, echo=FALSE, message=FALSE, warning=FALSE}
+# Load red light camera data and clean
+red_light_camera <- read_csv(here::here("inputs/data/red_light_camera.csv")) %>%
+  clean_names() %>%
+  select(activation_date, district) %>%
+  drop_na(activation_date) %>%
+  drop_na(district)
+
+# Create "year" variable
+red_light_camera$year <- vector("numeric", length = 199)
+for (i in 1:199){
+  red_light_camera$year[i]=format(as.Date(red_light_camera$activation_date[i], format="%Y/%m/%d"),"%Y")
+}
+
+# Create a table with selected columns
+red_light_camera %>%
+  select(district, year, activation_date) %>%
+  slice(1:10) %>%
+  kable(
+    caption = "Extracting the first ten rows from the Red Light Camera data",
+col.names=c("District", "Year", "Activation date"),
+linesep = "", digits = 1, booktabs=TRUE) %>%
+  kable_styling(latex_options = "HOLD_position", font_size = 10)
+```
+
+Table \@ref(tab:dadaextract1) shows the first ten rows of the Red Light Camera data in Toronto.
+"Year" is a new variable added by me into this dataset.
+It is pulled from the original variable "activation date", and it provides the year in which the red light camera is activated.
+Variable "District" includes the four main districts of Toronto: Toronto and East York, North York, Scarborough, and Etobicoke York.
+
+I'm interested in observing the cumulative number of red light cameras installed in each district from 2006 to 2020 and compare this data with the trend of number of motor vehicle collisions to see if they actually have connections.
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Number of red light cameras in the four districts each year", fig.width=7, fig.height=3.2}
+# Create a new dataset that presents the total number of red light cameras in each district
+red_light_camera <- red_light_camera %>%
+  filter(year != 2021)
+cumulative <-tibble(
+  year=c(2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020),
+  sum=c(0, 2, 6, 15, 16, 17, 17, 17, 17, 17, 17, 31, 33, 33, 34, 0, 0, 7, 17, 18, 18, 18, 18, 18, 18, 18, 42, 43, 44, 44, 0, 3, 10, 18, 19, 19, 19, 19, 19, 19, 19, 26, 27, 28, 28, 0, 1, 9, 15, 15, 15, 15, 15, 15, 15, 15, 36, 38, 41, 41),
+  district=c("Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Toronto and East York", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "Scarborough", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "North York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York", "Etobicoke York")
+)
+
+#Create a line plot from the dataset
+ggplot( aes(x=year, y=sum, group=district, color=district), data=cumulative) +
+    geom_line()+ylab("number of red light cameras")+theme_light()
+```
+
+Figure 3 demonstrates the total number of red light cameras in each district from 2006 to 2020.
+Scarborough installed the most red light cameras in this period of time, especially after 2016, a large number of red light cameras were installed there.
+The district of North York, on the contrary, started with the most red light cameras installed among all districts, but has the slowest growth and ended up with the least number of red light cameras in 2020 among all districts.
+All the four districts installed a large number of red light cameras from 2016 to 2017.
+
+I wanted to see how the increase in number of red light cameras compare with the traffic collision's frequency in each district.
+So, I selected the accidents that occurred at intersections or somewhere near intersections from the Motor Vehicle Collision dataset and created a bar plot to see their trend by each district in Toronto.
+
+```{r echo=FALSE, warning=FALSE, fig.cap="Comparing the number of motor vehicle collisions take place at or near intersections by district", fig.width=7, fig.height=3.2}
+# Select the accidents that only occur at or near intersections
+co <- vehicle_collision %>%
+  filter(accloc == "At Intersection" | accloc == "Intersection Related") %>%
+  drop_na(district)
+for(i in 1:9039){
+  if(co$district[i] == "Toronto East York"){
+    co$district[i] = "Toronto and East York"
+  }
+}
+
+# Create bar plot to compare vehicle collisions by districts
+ggplot(data=co,aes(x=year, fill=acclass))+geom_bar()+facet_wrap(~district)+ylab("number of motor vehicle collisions")+theme_light()+scale_fill_discrete(name = "Fatality")
+```
+
+Figure 4 shows the number of annual motor vehicle accidents occurred at or near intersections in each district.
+For all the districts, the numbers of fatal vehicle collisions stay approximately the same throughout these years, with Scarborough having the highest mortality rate in general.
+With regards to the total number of accidents, data in Etobicoke York, North York, and Scarborough all has its fluctuations, but the number remains about the same.
+The number of vehicle collisions in Toronto and East York was the highest in 2006, with more than to 260 cases, but it is the only district where the number has dropped.
+
+By comparing Figure 3 and Figure 4, I found that they haven't show any associations between the number of traffic accidents and the number of red light cameras installed.
+For instance, Scarborough has installed the most number of red light cameras, especially after the year of 2016, but its number of traffic accidents didn't reduced at all, it even reach its peak in 2018, nor did the fatality of those accidents.
+We see a large decrease in Toronto and East York's motor vehicle collisions, but it didn't installed at much red cameras as Etobicoke York or Scarborough.
+
+# Discussion
+
+The analysis of the two datasets shows no relationship between the cases of motor vehicle collisions in Toronto and the number of red light cameras.
+From the comparison between Figure 3 and Figure 4, we see that in none of the districts did the number of vehicle collisions followed the trend of the installations of the red light cameras.
+For instance, between 2016 and 2017, all four districts made the installations of lots of new red light cameras, but none of the bar plot in Figure 4 seemed to reflect that action.
+The implication of Section \@ref(data) is that: installing more red cameras does not change the number of traffic accidents in Toronto, nor does it influence the fatality of the accidents.
+A very likely reason to explain this situation is that red light cameras only concerned the drivers who already followed the rule most of the time, but not the rule-breaking drivers.
+Another possible reason would be that at intersections with red light cameras, more drivers would intend to stop rather than to proceed when they see the light is about to turn red, resulting in a higher chance of rear end accidents [@cite2].
+
+In recent years, complaints have been raised about whether red light cameras are used mainly to prevent injuries and deaths from traffic accidents or earn revenues for the government [@cite3].
+Measures should be taken to improve the effectiveness of this system and to ensure the safety of the drivers and pedestrians who are victims of the vehicle accidents.
+For instance, drivers should be more notified on the existence of red light cameras instead of knowing that after they are fined, because red light cameras are supposed to prevent severe accidents from happening but not to punish people after they cause the accidents.
+Government could also seek for other solutions to reduce those vehicle collisions.
+Toronto and East York has done a great job reducing the number of traffic collisions from 2006 to 2020, which means that other district could adopt similar traffic controls and see how it works in a few years.
+
+\newpage
+
+# References

### 2024-01-24 00_simulate.R

@@ -1,0 +1,23 @@
+
+#simulation
+#### Simulate ####
+set.seed(853)
+
+simulated_occupancy_data <-
+  tibble(
+    date = rep(x = as.Date("2021-01-01") + c(0:364), times = 3),
+    # Based on Eddelbuettel: https://stackoverflow.com/a/21502386
+    shelter = c(
+      rep(x = "Shelter 1", times = 365),
+      rep(x = "Shelter 2", times = 365),
+      rep(x = "Shelter 3", times = 365)
+    ),
+    number_occupied =
+      rpois(
+        n = 365 * 3,
+        lambda = 30
+      ) # Draw 1,095 times from the Poisson distribution
+  )
+
+head(simulated_occupancy_data)
+

### 2024-01-24 script/01_downloaddata.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Get data on 2021 shelter usage and make table
-# Author: Rohan Alexander
-# Email: rohan.alexander@utoronto.ca
-# Date: 1 July 2022
+# Purpose: Active Affordable and Social Housing Units
+# Author: Ziyi Liu
+# Email: jacqueline.liu@mail.utoronto.ca
+# Date: 23 January 2024
 # Prerequisites: -
 
 #### Workspace setup ####
@@ -17,23 +17,26 @@ library(janitor)
 library(lubridate)
 library(opendatatoronto)
 library(tidyverse)
+packages <- list_packages(limit = 10)
+packages
 
 
 #### Acquire ####
-toronto_shelters <-
-  # Each package is associated with a unique id  found in the "For 
-  # Developers" tab of the relevant page from Open Data Toronto
-  # https://open.toronto.ca/dataset/daily-shelter-overnight-service-occupancy-capacity/
-  list_package_resources("21c83b32-d5a8-4106-a54f-010dbe49f6f2") |>
-  # Within that package, we are interested in the 2021 dataset
-  filter(name == 
-           "daily-shelter-overnight-service-occupancy-capacity-2021.csv") |>
-  # Having reduced the dataset to one row we can get the resource
-  get_resource()
+toronto_housing <- search_packages("housing")
+toronto_housing
+housing1 <- list_package_resources("active-affordable-and-social-housing-units")
+housing1
+
+housing_file <- housing1 %>% 
+  filter(name == "Social and Affordable Housing.csv") 
+
+View(housing_file)
+housing_data <- get_resource(housing_file)
 
 write_csv(
-  x = toronto_shelters,
-  file = "toronto_shelters.csv"
+  x = toronto_housing,
+  file = "toronto_housing.csv"
 )
 
-head(toronto_shelters)
+head(toronto_housing)
+                                                                                            

### 2024-01-24 output/paper.rmd
dhd d

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "This paper delves into the multifaceted urban landscape of Toronto, focusing on the challenges and strategic responses linked with affordable and social housing.Toronto is one of the most populus and diverse cities in North Ameriva, it acts as a unique case study to examine urban housing dynamics.
-This research emoloys several dataset that p"
+abstract: "This paper delves into the multifaceted urban landscape of Toronto, focusing on the challenges and strategic responses linked with affordable and social housing.Toronto is one of the most populus and diverse cities in North America, it acts as a unique case study to examine urban housing dynamics.
+This research emoloys several dataset that include aspects such as affordable housing development, social housing waitlists and rental unit redevelopment.
+These findings reveal a complex housing landscape.
+The paper concludes with strategic recommendations for policy makers."
 output:
@@
 
-As one of the busiest and most modern city in Canada, Toronto constantly faces a large number of citizens, and, inevitably, heavy traffic.
-The road condition in Toronto is busy most of the time.
-The vast majority of roads and buildings under construction that take place almost everywhere narrow the roadway of vehicles and turn off traffic lights [@cite4].
-Heavy traffic is likely to be one of the main reasons behind car accidents, because it increases the road rage and encourages the vehicle drivers to make dangerous moves to save time.
-Vehicle collisions have always brought large financial costs to the involving parties, and even more, they even brought injuries and deaths.
-In just 2019, traffic accidents resulted in more than 1700 deaths and more than 140000 injuries [@cite1].
-
-The Motor Vehicle Collisions data of Toronto provides a record of the past severe vehicle collisions in Toronto which result in injuries or deaths, and with the help of statistical data analysis, it can possibly offer insights on the ways to reduce this type of accident.
-This report investigates the motor vehicle collisions in Toronto from 2006 to 2020, with a focus on the ones result in injuries or deaths.
-In Section \@ref(motor-vehicle-collisions-involving-killed-or-seriously-injured-persons), the Motor Vehicle Collisions dataset is introduced and organized to visualize the change in the annual number of traffic accidents with respect to their fatality and their location.
-Then, I discussed about the possible implications of these visualizations.
-Figure 1 showed that there was a descending trend of traffic accidents from 2006 to 2020.
-By Figure 2, I concluded that motor vehicle collisions are always more likely to occur at intersections.
-Thus, I brought out the Red Light Cameras dataset in Section \@ref(red-light-cameras) to see whether if the number of red light cameras has an effect on the number of traffic accidents with serious injuries and deaths.
-The result from the datasets indicates that there is no clear relationship between this two factors, suggesting that just by installing more red light cameras cannot prevent traffic accidents from happening at intersections.
-More implications and further discussions on this result is presented in Section \@ref(discussion).
+In exploring urban housing dynamics, we delve into the housing issues as reflected in the diverse datasets of Toronto's housing sector.
+This paper focuses in Toronto where it grappling with diverse housing challenges exacerbated by rapid urbanization and demographic shifts.
+With the data of rental housing transformation, affordable housing development, and the dynamics of social housing waitlists, this paper presents an analytical narrative on Toronto's evolving housing landscape.
+It examines how the city's policies and initiatives respond to the pressing needs for affordable and social housing, and discovering the challenges posed by urban growth, demographic changes, and economic pressures.
 
@@
 # Load red light camera data and clean
-red_light_camera <- read_csv(here::here("inputs/data/red_light_camera.csv")) %>%
+red_light_camera <- read_csv(here::here("toronto_housing.csv")) %>%
   clean_names() %>%

### 2024-01-24 output/paper.rmd
work

@@
 ---
-title: "Exploring Urban Housing Dynamics: Challenges and Strategies in Toronto's Affordable and Social Housing Landscape"
+title: "Evaluating Public Health Standards in Toronto: An Analysis of BodySafe Inspection Data"
 author: 
@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "This paper delves into the multifaceted urban landscape of Toronto, focusing on the challenges and strategic responses linked with affordable and social housing.Toronto is one of the most populus and diverse cities in North America, it acts as a unique case study to examine urban housing dynamics.
-This research emoloys several dataset that include aspects such as affordable housing development, social housing waitlists and rental unit redevelopment.
-These findings reveal a complex housing landscape.
-The paper concludes with strategic recommendations for policy makers."
+abstract: "This study presents a comprehensive analysis of public health inspection data from Toronto's BodySafe program, aiming to evaluate the safety standards to personal service in the city.
+We examine the trends in public health standards including spas, salons and tatto parlors.
+We focuses on infraction categories, inspection outcomes, and the impact of enforcement actions.
+By investigating the correlation between service types, inspection results, and geographic distribution, this study provides insights of effectiveness of public health policies and the implementation.
+This paper not onlt focus on the effectiveness of BodySafe program but also investigating potential opportunities to enhance public health safety."
 output:
@@
 # Introduction
-
-In exploring urban housing dynamics, we delve into the housing issues as reflected in the diverse datasets of Toronto's housing sector.
-This paper focuses in Toronto where it grappling with diverse housing challenges exacerbated by rapid urbanization and demographic shifts.
-With the data of rental housing transformation, affordable housing development, and the dynamics of social housing waitlists, this paper presents an analytical narrative on Toronto's evolving housing landscape.
-It examines how the city's policies and initiatives respond to the pressing needs for affordable and social housing, and discovering the challenges posed by urban growth, demographic changes, and economic pressures.
 

### 2024-01-24 script/01_downloaddata.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Active Affordable and Social Housing Units
+# Purpose: Toronto body safe
 # Author: Ziyi Liu
 # Email: jacqueline.liu@mail.utoronto.ca
 # Date: 23 January 2024
@@ -17,26 +17,21 @@ library(janitor)
 library(lubridate)
 library(opendatatoronto)
 library(tidyverse)
-packages <- list_packages(limit = 10)
+packages <- list_packages(limit = 50)
 packages
 
-
 #### Acquire ####
-toronto_housing <- search_packages("housing")
-toronto_housing
-housing1 <- list_package_resources("active-affordable-and-social-housing-units")
-housing1
-
-housing_file <- housing1 %>% 
-  filter(name == "Social and Affordable Housing.csv") 
-
-View(housing_file)
-housing_data <- get_resource(housing_file)
+toronto_bodysafe <-
+  list_package_resources("c4052ff7-a09d-4eaf-84e6-6669519f413d") |>
+  # Within that package, we are interested in the 2021 dataset
+  filter(name == 
+           "bodysafe - 4326.csv") |>
+  # Having reduced the dataset to one row we can get the resource
+  get_resource()
 
 write_csv(
-  x = toronto_housing,
-  file = "toronto_housing.csv"
+  x = toronto_bodysafe,
+  file = "toronto_bodysafe.csv"
 )
 
-head(toronto_housing)
-                                                                                            
+head(toronto_bodysafe)

### 2024-01-24 script/02_cleandata.R

@@ -1,20 +1,15 @@
 library(readr)
 library(dplyr)
 library(lubridate)
+library(tidyr)
 
-# Read the dataset
-toronto_housing_data <- read_csv("toronto_housing.csv")
+# Read the data
+data <- read.csv("toronto_bodysafe.csv")
 
-# Clean the data
-toronto_housing_data_cleaned <- toronto_housing_data %>%
-  select(-civic_issues) %>%
-  mutate(last_refreshed = ymd(last_refreshed))
+data_cleaned <- data %>% distinct()
 
-# View the cleaned data
-head(toronto_housing_data_cleaned)
+data_cleaned <- na.omit(data_cleaned)
 
-write_csv(
-  x = toronto_housing_data_cleaned,
-  file = "cleaned_toronto_housing.csv"
-)
+data_cleaned$insDate <- as.Date(data_cleaned$insDate)
 
+write.csv(data_cleaned, "toronto_bodysafe_cleaned.csv", row.names = FALSE)

### 2024-01-24 script/02_cleandata.R
ff

@@ -13,3 +13,4 @@ data_cleaned <- na.omit(data_cleaned)
 data_cleaned$insDate <- as.Date(data_cleaned$insDate)
 
 write.csv(data_cleaned, "toronto_bodysafe_cleaned.csv", row.names = FALSE)
+

### 2024-01-25 output/paper.qmd
bhh

---
title: "Evaluating Public Health Standards in Toronto: An Analysis of BodySafe Inspection Data"
author: 
  - Ziyi Liu
thanks: "Code and data are available at: https://github.com/liuziy23/Ziyi-Liu.git"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This study presents a comprehensive analysis of public health inspection data from Toronto's BodySafe program, aiming to evaluate the safety standards to personal service in the city. We examine the trends in public health standards including spas, salons and tatto parlors. We focuses on infraction categories, inspection outcomes, and the impact of enforcement actions. By investigating the correlation between service types, inspection results, and geographic distribution, this study provides insights of effectiveness of public health policies and the implementation. This paper not onlt focus on the effectiveness of BodySafe program but also investigating potential opportunities to enhance public health safety."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: reference.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set up libraries
library(tidyverse)
library(janitor)
```

\newpage

# Introduction

This paper offers a comprehensive exploration into the Toronto's public health conditions through the BodySafe inspection data. We examine the hygiene and safety standards for several public services such as tattoo parlors, beauty salons, and spas[@citedata]. These public services are considerably popular among women and it may result in safety hazard such as skin penetration due to the chemical exposures[@cite1]. The primary goal of BodySafe is to minimize the risk of infections and promote safe practices in environment where the services involce close contact or shared equipment. Also, BodySafe plays a crucial role in protecting public and workers and maintaining consumer confidence in the safe environment across Toronto [@cite2].

# Data

## Inspection Status Counts by Service Type in Toronto Bodysafe Establishments

The graph represents the frequency of diffrent inspection statuses across various service types in Toronto's BodySafe establishments [@citedata]. This will provide insights into how different types of estabilishments fare in inspections. The bar chart visually represents the number of different inspection statuses for various service types in Toronto Bodysafe estabilishments. Each bar represents a different service type, such as Nails, Aesthetics, Tattooing, etc., and is segmented by inspection status like pass, conditional pass, or fail.The service type with a high proportion of "pass" statuses have better health and safety standards, whereas the service type with "conditional pass" or "fail" indicate the improvements action they need to take.

The chart might also reveal trends specific for particular types of services. For example, some services might have more challenges in meeting the standard becuase the nature of the work, and it has a higher possibility to reieve conditional passes or fails.

This dataset contains 3365 inspections of various establishments such as beauty salons, spas, and tattoo parlors across Toronto. By using R [@citeR], an extract of the cleaned dataset (Table \@ref(tab:dataextract)) is shown below.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

plot_data <- as.data.frame(table(data$srvType, data$insStatus))

ggplot_plot <- ggplot(plot_data, aes(Var1, Freq, fill = Var2)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Inspection Status Counts by Service Type in Toronto Bodysafe Establishments",
       x = "Service Type",
       y = "Count of Inspections",
       fill = "Inspection Status") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(ggplot_plot)
```

We can also explore the number of inspections conducted over time in Toronto's BodySafe establishments, and we can see the trends and patterns of the frequency of the inspections.

```{r echo=FALSE, fig.cap="Comparing the location of traffic collisions each year from 2006 to 2020", fig.width=6, fig.height=3.2}
library(ggplot2)
library(lubridate)
library(dplyr)

data <- read.csv("toronto_bodysafe.csv")

# Convert the 'insDate' column to a Date type
data$insDate <- ymd(data$insDate)

# Aggregate data by month
monthly_inspection_data <- data %>%
  count(month = floor_date(insDate, "month"))

# Plotting the data
ggplot(monthly_inspection_data, aes(x = month, y = n)) +
  geom_line(color = 'teal') +
  geom_point(color = 'darkblue') +
  labs(title = 'Number of Inspections Over Time in Toronto BodySafe Establishments',
       x = 'Date (Month-Year)',
       y = 'Number of Inspections') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Discussion

\newpage

# References

### 2024-01-25 script/01_downloaddata.R

@@ -25,7 +25,7 @@ toronto_bodysafe <-
   list_package_resources("c4052ff7-a09d-4eaf-84e6-6669519f413d") |>
   # Within that package, we are interested in the 2021 dataset
   filter(name == 
-           "bodysafe - 4326.csv") |>
+           "bodysafe li- 4326.csv") |>
   # Having reduced the dataset to one row we can get the resource
   get_resource()
 

### 2024-01-25 01_downloaddata.R
delete

@@ -1,41 +1,0 @@
-#### Preamble ####
-# Purpose: Active Affordable and Social Housing Units
-# Author: Ziyi Liu
-# Email: jacqueline.liu@mail.utoronto.ca
-# Date: 23 January 2024
-# Prerequisites: -
-
-#### Workspace setup ####
-install.packages("opendatatoronto")
-install.packages("knitr")
-install.packages("janitor")
-install.packages("lubridate")
-install.packages("tidyverse")
-
-library(knitr)
-library(janitor)
-library(lubridate)
-library(opendatatoronto)
-library(tidyverse)
-packages <- list_packages(limit = 10)
-packages
-
-
-#### Acquire ####
-toronto_housing <- search_packages("housing")
-toronto_housing
-housing1 <- list_package_resources("active-affordable-and-social-housing-units")
-housing1
-
-housing_file <- housing1 %>% 
-  filter(name == "Social and Affordable Housing.csv") 
-
-View(housing_file)
-housing_data <- get_resource(housing_file)
-
-write_csv(
-  x = toronto_housing,
-  file = "toronto_housing.csv"
-)
-
-head(toronto_housing)

### 2024-01-25 02_cleandata.R

@@ -1,20 +1,0 @@
-library(readr)
-library(dplyr)
-library(lubridate)
-
-# Read the dataset
-toronto_housing_data <- read_csv("toronto_housing.csv")
-
-# Clean the data
-toronto_housing_data_cleaned <- toronto_housing_data %>%
-  select(-civic_issues) %>%
-  mutate(last_refreshed = ymd(last_refreshed))
-
-# View the cleaned data
-head(toronto_housing_data_cleaned)
-
-write_csv(
-  x = toronto_housing_data_cleaned,
-  file = "cleaned_toronto_housing.csv"
-)
-

### 2024-01-25 script/01_downloaddata.R
dele

@@ -5,7 +5,7 @@
 # Date: 23 January 2024
 # Prerequisites: -
 
-#### Workspace setup ####
+#### Workspace setup ####0
 install.packages("opendatatoronto")
 install.packages("knitr")
 install.packages("janitor")

### 2024-01-25 paper1.Rmd
change

--- 2024-01-25 output/paper.qmd
@@
 This paper not onlt focus on the effectiveness of BodySafe program but also investigating potential opportunities to enhance public health safety."
-output:
-  bookdown::pdf_document2
+output: pdf_document
 toc: TRUE
@@
 
-plot_data <- as.data.frame(table(data$srvType, data$insStatus))
+data <- utils::read.csv("toronto_bodysafe.csv")
+plot_data <- utils::as.data.frame(utils::table(data$srvType, data$insStatus))
 
@@
 data <- read.csv("toronto_bodysafe.csv")
-
 # Convert the 'insDate' column to a Date type
@@
 ggplot(monthly_inspection_data, aes(x = month, y = n)) +
-  geom_line(color = 'teal') +
+  geom_line(color = '#008080') +  
   geom_point(color = 'darkblue') +
@@
 
+The graph shows fluctuations in the number of inspections conducted over time in Toronto's Bodysafe establishments.
+Also, the data is added every month and offers the insight into trends and patterns of the frequency of inspections.The reason for these fluctuations are possibily due to policy changes, resource ability and seasonal variations.
+The peaks in the graph also indicate the months that have higher number of inspections.
+These might correspond to increase in regulatory activity or specific campaigns.
+In addition, the period where has less inspections indicate less activities due to holidays [@cite1].
+
 # Discussion

### 2024-01-25 output/paper.Rmd
final

--- 2024-01-25 paper1.Rmd
@@
 We examine the trends in public health standards including spas, salons and tatto parlors.
-We focuses on infraction categories, inspection outcomes, and the impact of enforcement actions.
-By investigating the correlation between service types, inspection results, and geographic distribution, this study provides insights of effectiveness of public health policies and the implementation.
-This paper not onlt focus on the effectiveness of BodySafe program but also investigating potential opportunities to enhance public health safety."
+We focuses on infraction categories, inspection outcomes.
+By investigating the correlation between service types, inspection results, and geographic distribution, this study provides insights of public health inspection results and variations in the frequency of inspections carried out over time at establishments regulated by Toronto's BodySafe program."
 output: pdf_document
@@
 ---
-
 ```{r setup, include=FALSE}
@@
 ```
-
-\newpage
 
@@
 Also, BodySafe plays a crucial role in protecting public and workers and maintaining consumer confidence in the safe environment across Toronto [@cite2].
+
+\newpage
 
@@
 data <- utils::read.csv("toronto_bodysafe.csv")
-plot_data <- utils::as.data.frame(utils::table(data$srvType, data$insStatus))
+plot_data <- as.data.frame(table(data$srvType, data$insStatus))
 
@@
 ```
+
+\newpage
+
+## The Number of Inspections Conducted Over Time in Toronto's BodySafe Establishments
 
@@
 
+The findings from analysis of Toronto's BodySafe inspection data provide several compelling insights into public health management in personal service settings.
+By increasing awareness among consumers about the standards they expect, we can drive demand for compliance and encourage a culture with safety and remain hygiene.
+These actions not only reinforce the importance of programs such as BodySafe in safeguarding public health but also suggest the services with further research and policy development to enhance their efficacy.
+Public health is still a challenging topic and personal service should be inspected and remain safe.
+
 \newpage

### 2024-01-25 script/00_simulate.R
1

@@ -1,23 +1,0 @@
-
-#simulation
-#### Simulate ####
-set.seed(853)
-
-simulated_occupancy_data <-
-  tibble(
-    date = rep(x = as.Date("2021-01-01") + c(0:364), times = 3),
-    # Based on Eddelbuettel: https://stackoverflow.com/a/21502386
-    shelter = c(
-      rep(x = "Shelter 1", times = 365),
-      rep(x = "Shelter 2", times = 365),
-      rep(x = "Shelter 3", times = 365)
-    ),
-    number_occupied =
-      rpois(
-        n = 365 * 3,
-        lambda = 30
-      ) # Draw 1,095 times from the Poisson distribution
-  )
-
-head(simulated_occupancy_data)
-
